---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<script defer src="https://use.fontawesome.com/releases/v5.0.8/js/all.js"></script>


# Tweets

Twitter is a an excellent source of information and humour, but keeping track of tweets is a difficult business. Until I have a better solution this repo includes two things:

- A screenshot of the tweet
- A link, description and categorisation of the tweet in `tweet-index.csv`

The table below is generated by `knitr::kable` and shows the tweets in reverse canonical order:

```{r tweets-table, echo=FALSE, message=FALSE, warning=FALSE}
library("tidyverse")
library("DT")
library("knitr")
library("lubridate")

tweets <- read_csv("data/tweet-index.csv")

subject_icons <- tribble(
  ~subject, ~icon,
  "reproducibility", "<span class='fas fa-recycle fa-2x'></span>",
  "scripting", "<span class='fas fa-file-code fa-2x'></span>",
  "data science", "<span class='fas fa-flask fa-2x'></span>",
  "data viz", "<span class='fas fa-chart-bar fa-2x'></span>"
)

colnames(tweets) <- make.names(tolower(colnames(tweets)))

tidy_tweets <- tweets %>%
  mutate(date.of.tweet = dmy(date.of.tweet),
         date.added = dmy(date.added),
         id = row_number()) %>%
  select(id, everything())


tidy_tweets %>%
  gather(subject, value, reproducibility:data.science) %>%
  filter(value == TRUE) %>%
  left_join(subject_icons) %>%
  group_by(filename, description, date.of.tweet, tweet.url) %>%
  summarise(icons = paste(icon, collapse = "<br>")) %>%
  ungroup() %>%
  mutate(tweet = paste0("<a href='", tweet.url, "' target='_blank'>", "<img src='", filename, "' style='min-width:400px'></img>", "</a>")) %>%
  select(tweet, description, date.of.tweet, icons) %>%
  arrange(desc(date.of.tweet)) %>%
  kable(align = "c",
        col.names = c("Tweet", "Tweet description", "Date of tweet",
                      "Subject of tweet?"))
```


## Note on screenshots

Screenshots will be highly irregular as there is not Twitter provided API for converting Tweets to images.

Screenshots will differ in at least the following ways:

- Operating System
- Browser / Twitter application
- Screen resolution
- Position in feed Tweet is viewed
- Pixel size of the image

## Copyright

The ownership of tweets, particularly the issue of copyright infringement, is a complicated business. Despite it not having any legal weight to it, I would like to make clear: *all rights belong to their respective copyright holders*.

Please contact me with an Issue or email (martinjohnhadley@gmail.com) if you would like your content to be removed.